---
title: "Project 2"
subtitle: "Proposal"
authors: "Christopher Newell"
format: html
editor: visual
---

```{r load-packages, echo=FALSE}
#| label: load-pkgs
#| message: false
#| warning: false

library(tidyverse)
library(tidytext)
library(knitr)
library(janeaustenr) 
library(dplyr)
library(RCurl)
```

## Dataset

```{r load-data}
#| label: load-data
#| message: false

mtg_rules_url <- "https://media.wizards.com/2024/downloads/MagicCompRules%2020240308.txt"
mtg_rules <- RCurl::getURL(mtg_rules_url) %>% str_split("\r\n") %>%
  pluck(1)
glimpse(mtg_rules)

```

## Reason for Choosing this Dataset

The MTG rulebook is about 250 pages. Understanding the rules completely is hard enough as it is. The goal of this project is to make a tool that will display trends and patterns in the rules, to better understand what mechanics in the rules are correlated.

I want to make this tool for two main reasons. The first reason is that I’m curious about what patterns might emerge. The second reason is that I am looking for a framework to help develop a method of learning the game. For example, if mechanic A and mechanic B are correlated, and mechanic B and mechanic C are correlated, but A and C are not, then it stands to reason that learning mechanic A or C before mechanic B might make learning the game easier.

## Questions and Analysis Plan

I plan to do stuff lmao.

1.  Look at the patterns in the words.
2.  Make some visulizations & interactable things.
3.  Get some data on the actual MTG cards if I can learn to read JSON.
